### 2016-08-09 Engine.tex
继续撰写node merge部分(未完成)

As stated in the filter module, the filtering is based on the last
$k$-symbol block of the sliding window. In particular, for a position
$i$ of the text $T$, if some pattern $p_j$ starts at $i$, there must
be $Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
$Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
we can group the patterns according to their signatures: patterns with
the same signature are grouped together to form a sub-pattern-set, and
for each sub-pattern-set we build a (small) AMT. In addition, an index
table is adopted to allow the corresponding AMT be retrieved in $O(1)$
time by its signature. Now, the verification module is made up of an
index table as well as several small AMTs.

Particularly, once a suspicious position $i$ in $T$ is detected, the
value $Hash[T[i+lss-k,k]]$ is used as the index of the index table to
find the corresponding small AMT for verifying $i$. As the scale of
the AMT shrunk, the time for each verifying is reduced accordingly.

\subsubsection{Node Merge}
\label{sec:node merge}

The nodes in a path of AMT, each of which has only one key, can be
merged into one node. This technique can reduce both time and space
efficiency of the verification module. To illustrate this, consider
the pattern set $P={p_1=, p_2=,p_3=}$ and its corresponding AMT
constructed by the method presented in section . As shown in Fig , the
built AMT has three nodes, and each of nodes has only one key. This
AMT roughly takes bytes of memory ( bytes for the keys and 16 bytes
for the child pointers), however, if we combine the three nodes into
one, the keys will be merged into one string and the child pointers
are no long needed. The only issue needs to be addressed is to
distinguish the keys after they are merged.

>>>>

As stated in Section \ref{sec:filter}, the filtering is based on the
last $k$-symbol block of the substring in the sliding window. In
particular, for a position $i$ of the text $T$, if some pattern $p_j$
starts at $i$, there must be
$Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
$Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
we can group the patterns according to their signatures: patterns with
the same signature are grouped together to form a sub-pattern-set, and
for each sub-pattern-set we build a (small) AMT. In addition, an index
table is adopted to allow the corresponding AMT be retrieved in $O(1)$
time by its signature. Now, the verification module is made up of an
index table as well as several small AMTs.

In the filtering phase, once a suspicious position $i$ in $T$ is
detected, the value $Hash[T[i+lss-k,k]]$ will be used as the index of
the index table to find the corresponding small AMT for verifying. As
the scale of the AMT shrunk, the time for each verifying is reduced
accordingly.

\subsubsection{Node Merging}
\label{sec:node merge}

The nodes in a path of AMT, each of which has only one key, can be
merged into one node. This technique can reduce both time and space
efficiency of the verification module. To illustrate this, consider
the pattern set $P=\{p_1=e^6u^5sscc,\, p_2=e^6u^5,\, p_3=e^6\}$ and
its corresponding AMT constructed by Algorithm 1. As shown in Fig (a),
the built AMT has three nodes, and each contains only one key. In a
typical x86\_64 architecture, this implementation of AMT roughly takes
55 bytes of memory: 15 bytes for the keys, 16 bytes for the child
pointers and 24 bytes for the pointers to the matching
functions. However, if we combine the three keys into one string, the
three nodes can be merged into one node (Fig (b)), as a result, the
child pointers are no longer needed and the number of function
pointers is reduced from three to one. The merged node is another type
of tree node in addition to the types we have introduced in Section
\ref{subsec:nodes}.

The only problem is to distinguish among the keys after they are
concatenated, to address this issues, an \emph{length array} is used
to store the length of each key, where each array element takes only
one byte (using the \emph{unsigned char} type). From the length of
each key, we can split the original keys out, and searching the target
string in the merged node can be trivial.

In general, after node merging, the AMT contains only one merged node
which takes 26 bytes (15 bytes for the keys, 3 bytes for the length
array, and 8 bytes for the matching function pointer), thus, 29 bytes
are saved comparing with the original AMT.
